Bayesian Hierarchical Modeling: An Introduction and Reassessment

### 2022-11-14 manuscript.tex
Clarification code

  pdfauthor={Myrthe Veenman1, Angelika M. Stefan2, \& Julia M. Haaf2},

@@

\title{Bayesian Hierarchical Modeling: An Introduction and Reassessment}
\author{Myrthe Veenman\textsuperscript{1}, Angelika M. Stefan\textsuperscript{2}, \& Julia M. Haaf\textsuperscript{2}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Leiden University\\\textsuperscript{2} University of Amsterdam}

@@

\textcolor{blue}{In hierarchical analyses, the general or overall effect is sometimes called fixed effect, and the individual-specific deviations from this effect are in that case referred to random effects (Rouder \& Lu, 2005). We can also estimate individual effects, not as deviations from an overarching effect, but as effects for each individual, as obtained from a per-participant analysis. Therefore, more common terms that suit the interpretation of the analyses better are general effect, individual deviation, and individual effects instead of fixed and random effects. We will use the terms general effect, individual deviation, and individual effect throughout this tutorial.}

@@

\begin{equation}
\text{BF}_{\text{nl}} = \frac{\int_{-\infty}^{\infty}P(\bm{Y} | \mathcal{M}_\text{n}, \bm{\theta_{\text{n}}})f(\bm{\theta_{\text{n}}})d\bm{\theta_{\text{n}}}}{\int_{-\infty}^{\infty}P(\bm{Y} | \mathcal{M}_\text{l}, \bm{\theta_{\text{l}}})f(\bm{\theta_{\text{l}}})d\bm{\theta_{\text{l}}}}. 
\end{equation}

>>>>

  pdfauthor={Myrthe Veenman1, Angelika M. Stefan2, \& Julia M. Haaf3},

@@

\title{Bayesian Hierarchical Modeling: An Introduction and Reassessment}
\author{Myrthe Veenman\textsuperscript{1}, Angelika M. Stefan\textsuperscript{2}, \& Julia M. Haaf\textsuperscript{3}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Leiden University\\\textsuperscript{2} Universität der Bundeswehr München\\\textsuperscript{3} University of Amsterdam}

@@

\textcolor{blue}{In hierarchical analyses, the general or overall effect is sometimes called fixed effect, and the individual-specific deviations from this effect are in that case referred to as random effects (Rouder \& Lu, 2005). We can also estimate individual effects, not as deviations from an overarching effect, but as effects for each individual, as obtained from a per-participant analysis. Therefore, more common terms that suit the interpretation of the analyses better are general effect, individual deviation, and individual effects instead of fixed and random effects. We will use the terms general effect, individual deviation, and individual effect throughout this tutorial.}

@@

\begin{equation}
\text{BF}_{\text{nl}} = \frac{P(\bm{Y} | \mathcal{M}_n)}{P(\bm{Y} | \mathcal{M}_{\text{l}})} = \frac{\int_{-\infty}^{\infty}P(\bm{Y} | \mathcal{M}_\text{n}, \bm{\theta_{\text{n}}})f(\bm{\theta_{\text{n}}})d\bm{\theta_{\text{n}}}}{\int_{-\infty}^{\infty}P(\bm{Y} | \mathcal{M}_\text{l}, \bm{\theta_{\text{l}}})f(\bm{\theta_{\text{l}}})d\bm{\theta_{\text{l}}}}. 
\end{equation}
